# RESTful

* interoperability between computer systems on the Internet. 
* requesting systems to access and manipulate textual representations of Web resources 

Example:

https://api.ipify.org/?format=json

> curl -s 'https://api.ipify.org/?format=json'

```{r}
require(httr)
require(jsonlite)
require(magrittr)
require(tidyverse)

res <- GET("https://api.ipify.org/", query = list(format = 'json'))
content(res, type = "text", encoding = 'utf-8')
content(res, type = "text", encoding = 'utf-8') %>% fromJSON

content(res, type = "text", encoding = 'utf-8') %>% fromJSON %>% `[[`("ip")
```

More sophisticated example

API article: https://github.com/derhuerst/db-rest/blob/master/docs/index.md

https://1.db.transport.rest/stations?query=mannheim


```{r}
res <- GET("https://1.db.transport.rest/stations", query = list(query = 'mannheim'))
mannheim_sid <- content(res)[[1]]$id
res <- GET("https://1.db.transport.rest/stations", query = list(query = 'berlin'))
berlin_sid <- content(res)[[1]]$id

##https://1.db.transport.rest/journeys?from=8000244&to=8011160
res <- GET("https://1.db.transport.rest/journeys", query = list(from = mannheim_sid, to = berlin_sid))
```

# HTTP Methods

* GET
Regular web request from browser, query strings (parameters) encoded in the URL

* POST
Request with information / file, query not encoded in the URL

* DELETE / HEAD / PUT / ...

Example: https://developers.facebook.com/docs/graph-api/reference/page

# Facebook

https://graph.facebook.com/AngelaMerkel

Access token: your id, determining your right and measuring your usage.

https://developers.facebook.com/tools/explorer

```{r}

res <- GET("https://graph.facebook.com/AngelaMerkel")
content(res)
temptoken <- ""
res <- GET("https://graph.facebook.com/", path = "AngelaMerkel", query = list(access_token = temptoken))
content(res)
res <- GET("https://graph.facebook.com/", path = "AngelaMerkel/likes", query = list(access_token = temptoken))
res <- GET("https://graph.facebook.com/", path = "AngelaMerkel/feed", query = list(access_token = temptoken))
content(res)$data[[1]]$id
res <- GET("https://graph.facebook.com/", path = paste0(content(res)$data[[1]]$id, "/", "comments"), query = list(access_token = temptoken, fields = "from"))
```

Tedious!

## Abstractions

Rfacebook by Pablo Barberá (LSE).

```{r}
## devtools::install_github("pablobarbera/Rfacebook/Rfacebook")
require(Rfacebook)

AM <- getPage("AngelaMerkel", feed = TRUE, reactions = TRUE, token = temptoken, api = 'v2.8')
post <- getPost(AM$id[1], token = temptoken, n = 1000, likes = TRUE, comments = TRUE)
post$comments[1,]
```

## Longterm token

Facebook authentication

https://developers.facebook.com/apps

* add product: login
* add OA redirect URIs
* add site URL
* add App Domains

```{r}
app_id <- ""
app_secret <- ""
longtoken <- fbOAuth(app_id = app_id, app_secret = app_secret)
SPDposts <- getPage(page = "SPD", token = longtoken, n = 100, feed = TRUE)

post <- getPost(AM$id[1], token = longtoken, n = 1000, likes = TRUE, comments = TRUE)
post$comments[1,]
```

## SocialMediaLab

An R project created at The Virtual Observatory for the Study of Online Networks (VOSON) Lab at ANU by Tim Graham and Robert Ackland.

I contributed the ACC workflow to simpify the usage.

* Authenticate - API related authentication
* Collect - Data collection from social media APIs
* Create - Create networks from social media data

```{r}
devtools::install_github('vosonlab/SocialMediaLab/SocialMediaLab')
require(SocialMediaLab)
require(magrittr)
require(igraph)

Authenticate("facebook", appID = app_id, appSecret = app_secret, extendedPermissions = TRUE) %>% SaveCredential()
LoadCredential() %>% Collect(pageName = "SPD", rangeFrom = "2017-09-25", rangeTo = '2018-02-12') -> SPDdata
SPDdata %>% Create('Bimodal') -> SPDbimodal

### You can do it in a single pipeline
Authenticate("facebook", appID = app_id, appSecret = app_secret, extendedPermissions = TRUE) %>% Collect(pageName = "SPD", rangeFrom = "2017-09-25", rangeTo = '2018-02-12') %>% Create('Bimodal') -> SPDbimodal

plot(SPDbimodal, vertex.label = V(SPDbimodal)$username, vertex.color = ifelse(V(SPDbimodal)$type == "User", "Red", "White"))
SPD_commenters <- data.frame(username = V(SPDbimodal)$username[match(names(sort(degree(SPDbimodal, mode = 'out'), TRUE)), V(SPDbimodal)$label)], degree = as.vector(sort(degree(SPDbimodal, mode = 'out'), TRUE)))
SPD_commenters %>% filter(degree > 0)
```
